---
title: "Week 3/4 Assignment"
author: "Aum Brahmbhatt"
date: "April 28, 2021"
output: ioslides_presentation
---

```{r setup, include=FALSE,  message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(plotly)
library(tidyr)
```

## S&P 500 vs COVID IN U.S

- This presentation shows how S&P 500 reacts to covid cases in United States

- This analysis is only valid for United States. 

- S&P 500 Data was collected from finance.yahoo.com

- covid data was collected from covidtracking.com/data

## CODE USED TO DISPLAY THE GRAPH ON NEXT SLIDE
```{r, comment="", message = FALSE, warning = FALSE, eval=FALSE, echo=TRUE}
sp <- read.csv("sp500.csv")
sp <- sp[, c("Date", "Open")]
sp <- mutate(sp, Date = gsub(",", "", Date))
sp <- mutate (sp, Date = as.Date(Date, format = "%B %d %Y"))
sp <- mutate(sp, Date = as.character(Date))
sp <- mutate(sp, Open = as.numeric(gsub(",", "", Open)))
covid <- read.csv("covid.csv")
covid <- covid[, c("date", "positiveIncrease")]
covid <- mutate(covid, positiveIncrease = positiveIncrease/50)
final <- merge(sp, covid, by.x = "Date", by.y = "date")
final <- gather(final, key = "index", value = "value", -Date)
suppressWarnings(plot_ly(x = final$Date, y = final$value, 
                         type = 'scatter', 
                         mode = 'lines', 
        color = final$index))
```

## GRAPH S&P 500 PRICE VS INCREASE IN COVID CASES
```{r, comment="", message = FALSE, warning = FALSE}
sp <- read.csv("sp500.csv")
sp <- sp[, c("Date", "Open")]
sp <- mutate(sp, Date = gsub(",", "", Date))
sp <- mutate (sp, Date = as.Date(Date, format = "%B %d %Y"))
sp <- mutate(sp, Date = as.character(Date))
sp <- mutate(sp, Open = as.numeric(gsub(",", "", Open)))
covid <- read.csv("covid.csv")
covid <- covid[, c("date", "positiveIncrease")]
covid <- mutate(covid, positiveIncrease = positiveIncrease/50)
final <- merge(sp, covid, by.x = "Date", by.y = "date")
final <- gather(final, key = "index", value = "value", -Date)
suppressWarnings(plot_ly(x = final$Date, y = final$value, type = 'scatter', 
                         mode = 'lines', 
        color = final$index))
```

## CODEBOOK AND DATA MANIPULATION
- positiveIncrease: The daily increase in API field positive, which measures Cases (confirmed plus probable) calculated based on the previous day’s value.

- Open: The price at which S&P500 Opened. 

- On the Y-axis we have S&P500 Pricea and scaled value of PositiveIncrease. 

- On the X-axis we have dates from Jan 13, 2020 to March 5th, 2021. 

- P.S: In order to fit the covid data in the graph, the covid data was scaled down by dividing the positiveIncrease by 50. 

## CONCLUSION
- From the data, we can see a drop in S&P500 only when covid cases first started to rise

- Other than that, S&P500 is not affected by covid. 

